---
title: "DDP Wk4"
author: "David Silbermann"
date: "December 19, 2016"
output: ioslides_presentation
---


## Slide 2

For the Developing Data Products Week 4 assignment I developed a Shiny application that displays fictious points of interest in three cities, Baltimore, Boston, and New York.  Leaflet is used to map these points.

## Code to generate Points of Interest

To generate the fictious points of interest I use the `runif` funtion. Here's an example of the code that I used to generate the points around Boston.

```{r}

df <- data.frame(lat = runif(15, min = 42.3, max = 42.4),
        lng = runif(15, min = -71.1, max = -71.0))

head(df)
```

## And here's the code that I use to plot

```{r, eval=FALSE}
library(leaflet)

        df %>% 
           leaflet() %>%
           addTiles() %>%
           addMarkers()
```

## Sample Plot
```{r, warning=FALSE, echo=FALSE}
library(leaflet)

        df <- data.frame(lat = runif(15, min = 42.3, max = 42.4),
                lng = runif(15, min = -71.1, max = -71.0))

        df %>% 
           leaflet() %>%
           addTiles() %>%
           addMarkers()
```


